### 2013-10-07 abstract.tex
corrected Zach P75 dimension

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on their stiffness.  In this study, MR and ARFI imaging
datasets were compared to one another and with gross pathology measurements
made immediately post radical prostatectomy.  Images were manually segmented to
delineate the central gland (CG) and prostate capsule, and 3D models were
rendered to evaluate zonal anatomy dimensions and volumes.  Both imaging
modalities showed moderate correlations between estimated organ volume and
gross pathologic weights.  ARFI and MR total prostate gland volumes were
well-correlated (R$^2$ = 0.63), but ARFI images yielded prostate volumes that
were, on average, larger (6.1\% $\pm$ 25\%) than MR images, primarily due to
over-estimation of the lateral dimension of the total gland (13.5 $\pm$
11.0\%), while over-estimates of the other dimensions were less significant
(5.7 $\pm$ 20.6\% and -2.4 $\pm$ 17.0\%).  The ARFI and MR CG volumes were also
moderately correlated (R$^2$ = 0.38).  CG volume differences were attributed to
under-estimation of the anterior-to-posterior axis (-8.4 $\pm$ 24.0\%), and
over-estimation bias in the lateral dimension (11.5 $\pm$ 22.5\%).  ARFI
prostate imaging yielded prostate volumes and dimensions that were correlated
with MR T2WI estimates, with biases in the AP dimension, most likely related to
poor displacement SNR in the anterior region of the prostate from greater
distance from the rectal wall imaging surface.  Lateral dimension contrast was
also challenging due to peri-prostatic fat.  ARFI imaging is a promising
low-cost, real-time imaging modality that can compliment MR imaging for
diagnosis, treatment planning and management of PCa.

>>>>

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on their stiffness.  In this study, MR and ARFI imaging
datasets were compared to one another and with gross pathology measurements
made immediately post radical prostatectomy.  Images were manually segmented to
delineate the central gland (CG) and prostate capsule, and 3D models were
rendered to evaluate zonal anatomy dimensions and volumes.  Both imaging
modalities showed moderate correlations between estimated organ volume and
gross pathologic weights.  ARFI and MR total prostate gland volumes were
well-correlated (R$^2$ = 0.63), but ARFI images yielded prostate volumes that
were, on average, larger (6.1\% $\pm$ 25\%) than MR images, primarily due to
over-estimation of the lateral dimension of the total gland (13.5 $\pm$
11.0\%), while over-estimates of the other dimensions were less significant
(5.7 $\pm$ 20.6\% and 2.4 $\pm$ 17.0\%).  The ARFI and MR CG volumes were also
moderately correlated (R$^2$ = 0.38).  CG volume differences were attributed to
under-estimation of the anterior-to-posterior axis (-6.1 $\pm$ 21.1\%), and
over-estimation bias in the lateral dimension (11.5 $\pm$ 22.5\%).  ARFI
prostate imaging yielded prostate volumes and dimensions that were correlated
with MR T2WI estimates, with biases in the AP dimension, most likely related to
poor displacement SNR in the anterior region of the prostate from greater
distance from the rectal wall imaging surface.  Lateral dimension contrast was
also challenging due to peri-prostatic fat.  ARFI imaging is a promising
low-cost, real-time imaging modality that can compliment MR imaging for
diagnosis, treatment planning and management of PCa.

### 2013-10-07 conclusions.tex
corrected Zach P75 dimension

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = 0.63), but ARFI images yielded prostate volumes
that were, on average, larger (6.1\% $\pm$ 25\%) than MR images, primarily due
to over-estimation of the lateral dimension of the prostate total gland (13.5
$\pm$ 11.0\%), while over-estimates of the other dimensions were less
significant contributors (5.7 $\pm$ 20.6\% and -2.4 $\pm$ 17.0\%).  The central
zone volumes of ARFI and MR images were also moderately correlated (R$^2$ =
0.38), with minimal volume bias between the imaging modalities, but significant
variability case-to-case (-5.0 $\pm$ 39.5\%).  Central zone volume differences
were, again, strongly attributed to over-estimation of the lateral dimension
(11.5 $\pm$ 22.5\%), with a significant underestimation of the
anterior-to-posterior dimension (-8.4 $\pm$ 24.0\%).  Strong variability in
central gland volumes is believed to be related to the extent of benign
prostatic hyperplasia (BPH) for select cases.  Overall, ARFI imaging of the
prostate yielded prostate volumes and dimensions that were correlated with MR
T2WI estimates, with biases in the anterior-to-posterior dimension, most likely
related to poor displacement SNR in the anterior region of the prostate from
greater distance from the rectal wall imaging surface, and the lateral
dimension, where contrast between the PZ and peri-prostatic fat could be
limited.  ARFI imaging is a promising low-cost, real-time imaging modality that
can compliment MR imaging for diagnosis, treatment planning and management of
PCa.

>>>>

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = 0.63), but ARFI images yielded prostate volumes
that were, on average, larger (6.1\% $\pm$ 25\%) than MR images, primarily due
to over-estimation of the lateral dimension of the prostate total gland (13.5
$\pm$ 11.0\%), while over-estimates of the other dimensions were less
significant contributors (5.7 $\pm$ 20.6\% and 2.4 $\pm$ 17.0\%).  The central
zone volumes of ARFI and MR images were also moderately correlated (R$^2$ =
0.38), with minimal volume bias between the imaging modalities, but significant
variability case-to-case (-5.0 $\pm$ 39.5\%).  Central zone volume differences
were, again, strongly attributed to over-estimation of the lateral dimension
(11.5 $\pm$ 22.5\%), with a significant underestimation of the
anterior-to-posterior dimension (-6.1 $\pm$ 21.1\%).  Strong variability in
central gland volumes is believed to be related to the extent of benign
prostatic hyperplasia (BPH) for select cases.  Overall, ARFI imaging of the
prostate yielded prostate volumes and dimensions that were correlated with MR
T2WI estimates, with biases in the anterior-to-posterior dimension, most likely
related to poor displacement SNR in the anterior region of the prostate from
greater distance from the rectal wall imaging surface, and the lateral
dimension, where contrast between the PZ and peri-prostatic fat could be
limited.  ARFI imaging is a promising low-cost, real-time imaging modality that
can compliment MR imaging for diagnosis, treatment planning and management of
PCa.

### 2013-10-07 results.tex
corrected Zach P75 dimension

Measurements of the prostate total and CG dimensions along the three
standard anatomic axes (apex-to-base, lateral-to-lateral, and
anterior-to-posterior) were made (Table~\ref{tab:mr_arfi_axes}), and the
correlation between the imaging axis measurements was analyzed
(Figure~\ref{fig:mr_arfi_path_axes}).  ARFI was most correlated to MR in the
lateral-to-lateral axis in both the total and CG (R$^2$ = 0.57 and
0.32, respectively), with mean overestimates of 13.5 $\pm$ 11.0\% and 11.5 $\pm$
22.5\%, respectively (Table~\ref{tab:mr_arfi_axes_error}).  ARFI had moderate
correlation with the total prostate gland axis in the anterior-to-posterior
dimension (R$^2$ = 0.23), but poor correlation in the CG (R$^2$ =
0.00), with overestimates of 5.7 $\pm$ 20.6 and -8.4 $\pm$ 24.0\%.  ARFI
imaging had weak correlation with MR images in the apex-to-base dimension
(R$^2$ = 0.19, total gland and R$^2$ = 0.09, CG), with differences
of -2.4 $\pm$ 17.0 and 1.2 $\pm$ 19.8\%, respectively.

>>>>

Measurements of the prostate total and CG dimensions along the three standard
anatomic axes (apex-to-base, lateral-to-lateral, and anterior-to-posterior)
were made (Table~\ref{tab:mr_arfi_axes}), and the correlation between the
imaging axis measurements was analyzed (Figure~\ref{fig:mr_arfi_path_axes}).
ARFI was most correlated to MR in the lateral-to-lateral axis in both the total
and CG (R$^2$ = 0.57 and 0.32, respectively), with mean overestimates of 13.5
$\pm$ 11.0\% and 11.5 $\pm$ 22.5\%, respectively
(Table~\ref{tab:mr_arfi_axes_error}).  ARFI had moderate correlation with the
total prostate gland and CG axes in the anterior-to-posterior dimension (R$^2$
= 0.23 and R$^2$ = 0.34), respectively, with overestimates of 5.7 $\pm$ 20.6
and -6.1 $\pm$ 21.1\%.  ARFI imaging had weak correlation with MR images in the
apex-to-base dimension (R$^2$ = 0.19, total gland and R$^2$ = 0.09, CG), with
differences of 2.4 $\pm$ 17.0 and 1.2 $\pm$ 19.8\%, respectively.
